Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-01-18 paper/aldebaran.tex
titles
got that accursed bounding box
caption
figure labels

\citet{Hatzes2015} reported on RV observations of Aldebaran from the coud\'{e}
\'{e}chelle spectrograph of the Th\"{u}ringer Landessternwarte Tautenburg (TLS), the
Tull Spectrograph of the McDonald 2.7 m telescope, and the Bohyunsan Observatory
\'{E}chelle Spectrograph (BOES) spectrograph of the Bohyunsan Optical Astronomy
Observatory (BOAO) spanning the period from 2000.01 to 2013.92.  Combined with earlier observations \citep{hatzes1993}, we construct a full time series spanning more than two decades and attempt to fit this with a Keplerian model and a CARMA noise process.

@@

In order to confirm the oscillations detected in the archival data, we used the Hertzsprung SONG telescope \citep{2017ApJ...836..142G} to conduct high time cadence follow-up observations. These were carried out in the highest resolution mode ($R\approx110000$)
with an integration time of 30\,s, between 2016 September 27 and 2017 January 12. During this time we attempted to obtain at least one
visit per available night, for a total of 254 epochs over the campaign. The spectra were
extracted using the SONG pipeline \citep[see][]{2017ApJ...836..142G}. SONG employs an iodine cell for
precise wavelength calibration and the velocities were determined using the \textit{iSONG}
software following the same procedures as described in \cite{2017ApJ...836..142G}. The typical
velocity precision per visit is 2.5$\,\rm m\,s^{-1}$ allowing us to easily detect the oscillations
which displays a peak-to-peak amplitude of $\approx \, 170 \, \rm m \, s^{-1}$. $\bf Figure XX$ show
the radial velocities obtained -- oscillations are easily visible as well as a long-term
trend, probably due to the planetary companion.

>>>>

\citet{Hatzes2015} reported on RV observations of Aldebaran from the coud\'{e}
\'{e}chelle spectrograph of the Th\"{u}ringer Landessternwarte Tautenburg (TLS), the
Tull Spectrograph of the McDonald 2.7 m telescope, and the Bohyunsan Observatory
\'{E}chelle Spectrograph (BOES) spectrograph of the Bohyunsan Optical Astronomy
Observatory (BOAO) spanning the period from 2000.01 to 2013.92.  Combined with earlier observations \citep{hatzes1993}, we construct a full time series spanning more than two decades (Figure~\ref{alldata}) and attempt to fit this with a Keplerian model and a CARMA noise process.

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{all-data.pdf}
\caption{All archival and new radial velocities used for inference in this work.}
\label{alldata}
\end{figure}

@@

In order to confirm the oscillations detected in the archival data, we used the Hertzsprung SONG telescope \citep{2017ApJ...836..142G} to conduct high time cadence follow-up observations. These were carried out in the highest resolution mode ($R\approx110000$)
with an integration time of 30\,s, between 2016 September 27 and 2017 January 12. During this time we attempted to obtain at least one
visit per available night, for a total of 254 epochs over the campaign. The spectra were
extracted using the SONG pipeline \citep[see][]{2017ApJ...836..142G}. SONG employs an iodine cell for
precise wavelength calibration and the velocities were determined using the \textit{iSONG}
software following the same procedures as described in \cite{2017ApJ...836..142G}. The typical
velocity precision per visit is 2.5$\,\rm m\,s^{-1}$ allowing us to easily detect the oscillations
which displays a peak-to-peak amplitude of $\approx \, 170 \, \rm m \, s^{-1}$. Figure~\ref{songdata} displays
the radial velocities obtained -- oscillations are easily visible as well as a long-term
trend, probably due to the planetary companion.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{song-data.pdf}
\caption{New radial velocities of Aldebaran obtained by the Hertzsprung~SONG Telescope. Clear oscillations can be seen, plus a trend representing part of the planetary orbit.}
\label{songdata}
\end{figure}
